\emph{Light Exposure Behavior Assessment (LEBA)}: Develop of a novel instrument to capture light exposure-related behaviours

### 2021-08-31 manuscript.Rmd

```{r setup, include = FALSE}
library(papaja) # devtools::install_github("crsh/papaja")
library(readr)
library(readxl)
library(lavaan)
library(semPlot)
library(semTools)
library(hemp) # devtools::install_github("cddesja/hemp")
library(psych)
library(dlookr)
library(tidyverse)
library(qgraph)
library(kableExtra)
library(DiagrammeR) #devtools::install_github('rich-iannone/DiagrammeR')
library(DiagrammeRsvg)
library(rsvg)
r_refs("r-references.bib")
```

@@

@@

# Results
```{r Normality assumption EFA}
LB <- read_excel("recoded not reversed_EFA.xlsx")
LB$X1 <- NULL
KMO <- KMO(LB)

```
Sampling adequacy was investigated by Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy[@kaiserIndexFactorialSimplicity1974] . The overall KMO vale for 23 items was `r printnum(KMO$MSA)` which was above the cutoff value of .50 indicating a mediocre sample [@hutchesonMultivariateSocialScientist1999].

>>>>

```{r setup, include = FALSE}
library(papaja) # devtools::install_github("crsh/papaja")
library(readr)
library(readxl)
library(lavaan)
library(semPlot)
library(semTools)
library(MOTE)
library(psych)
library(dlookr)
library(tidyverse)
library(qgraph)
library(kableExtra)
library(DiagrammeR) #devtools::install_github('rich-iannone/DiagrammeR')
library(DiagrammeRsvg)
library(rsvg)
r_refs("r-references.bib")
```

@@

### Data Collection
Timeline of data collection, ethical approval, mode of data collection, how consent was recorded.

### Item generation and Content Validity: Expert Panel Review
How we developed the 48 items?

@@

# Results
```{r Normality assumption EFA}
LB <- read_excel("recoded not reversed_EFA.xlsx")
LB$X1 <- NULL
#KMO test
KMO <- KMO(LB)

# Test of correlation matrix
bartlet <- cortest.bartlett(LB, n =428)

# Univariante normality
normality <- normality(LB)

# Multivariate Normality
mardia <- mardia(LB, na.rm = T, plot =F)

# Descriptives
Descriptives <- psych::describe(LB)
alpha <- psych::alpha(LB)
Item.total <- alpha$item.stats
Item.total$r.cor
Des.combined <- cbind(apa(Descriptives$mean,2,T), apa(Descriptives$sd,2,T), apa(Descriptives$skew,2,T),apa(Descriptives$kurtosis,2,T), apa(normality$statistic,2,T), apa(normality$p_value,2,F), apa(Item.total$r.cor,2,F))
colnames(Des.combined) = c("Mean", "SD", "Skew", "Kurtosis", "Shapiro-Wilk Statistics", "p", "Item-Total Correlation")
rownameprefix <- "Item"
rownamesufix <- seq(1:48)
my.names <- paste(rownameprefix,rownamesufix, sep = "" )
rownames(Des.combined) = (my.names)

#Polychoric Correlation matrix
LB.factor <- sapply(LB, as.factor)
correlations <- polychoric(LB.factor, correct = 0)

BigR = sum(correlations$rho >= abs(.30) & correlations$rho < abs(1.0), na.rm =T)/2 
totR = length(LB)*(length(LB)-1)/2
A <- print (BigR/totR)*100

# Item analysis
Item_analysis <- psych::alpha(LB)
Item_analysis$item.stats$r.cor
R.cor.sum <- summary(Item_analysis$item.stats$r.cor)
low.r.cor <- abs(R.cor.sum[1])
high.r.cor <- R.cor.sum[6]
```
Sampling adequacy was investigated by Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy[@kaiserIndexFactorialSimplicity1974] . The overall KMO vale for 23 items was `r printnum(KMO$MSA)` which was above the cutoff value of .50 indicating a mediocre sample [@hutchesonMultivariateSocialScientist1999].

```{r tabDes, results='asis'}
apa_table(Des.combined, caption = "Descriptive Statistics")
```

Table\@ref(tab:tabDes) summarizes the univariate descriptive statistics for the 48 items. some of the items were skewed with high Kurtosis values. The Shapiro-Wilk test of normality [@shapiroAnalysisVarianceTest1965] indicated all the items violated normality assumptions. Multivariate normality assumptions were investigated by Marida's test [@mardiaMeasuresMultivariateSkewness1970]. Multivariate skew = `r printnum(mardia$b1p)` (p <0.001) and multivariate kurtosis = `r printnum(mardia$b2p)` (p <0.001) indicated  multivariate normality assumptions violation. Due to these violations and ordinal nature of the response data  polychoric correlations over Pearson's correlations was chosen [@desjardinsHandbookEducationalMeasurement2018]. Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954], $\chi^2$ (`r bartlet$df`) = `r apa(bartlet$chisq, 2, T)`, p < .001] indicated the correlations between items are adequate for the EFA. However only `r apa(((BigR/totR)*100), 2,T)`% of the inter-item correlation coefficients were greater than .30 in the obtained matrix. The corrected item-total correlations ranged between `r apa(low.r.cor,2,F)` to `r apa(high.r.cor,2,F)`.
